Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-01 paper/experiments.tex
minor changes
updates to multiple sections

%\begin{itemize}
%\item Describe Data for both Experiments
%\item Describe the Four different conditions
%\item Describe how they are all evaluated, with and without hierarchy
%\end{itemize}

@@

\subsubsection{Diagnosis Prediction}

@@

\subsubsection{Product Category Prediction}

In this experiment, we look at product descriptions and their
categorizations according to a product hierarchy. Product ID's
and categorizations were obtained from the Stanford Network Analysis Platform
(SNAP) dataset~\citep{SNAP}. Product descriptions were crawled from the
amazon.com website directly. We were able to deduce the structure of the
hierarchy for the Amazon.com products directly since all ancestors in the
hierarchy were included with each category label. For example, {}``DVD / Genres
/ Science Fiction \& Fantasy / Classic Sci-Fi'' is a single product category 
for the DVD, {}``The Time Machine.''

@@

We applied HSLDA, along with three other closely related models, to
the clinical data and the retail product data. Specifically, we evaluate
models including sLDA with independent regressors (hierarchical constraints
on labels ignored), HSLDA fit by performing LDA followed by tree-conditional
regressions, and HSLDA fit with fixed random regression parameters.
We will refer to the three comparison models as the sLDA model, the
separate HSLDA model, and the random HSLDA model, respectively. These
models were chosen as to highlight performance in absence of hierarchical
constraints, the effect of the combined inference procedure, and regression
performance attributable solely to the hierarchical constraints.

@@

%\begin{itemize}
%\item Talk about hierarchy and no hierarchy
%\item Make explicit calculation of sensitivity and 1-specificity
%\end{itemize}
For each dataset, a held out set of 1,000 documents and accompanying
labels were used for evaluation. The two main methods of evaluation
for the model are prediction and topic quality. To evaluate predictive
performance for all comparison models equivalently, each model was
evaluated with two methods. The first evaluation method augments the
observed labels in the held out set with their ancestors and considers
all other non-existant labels to be negative. The second method ignores
the ancestors of the observed labels in the held out set and considers
all other non-existant labels to be negative. This uniform treatment
of ancestors allows for a fair comparison of the models.

>>>>

@@

\subsubsection{Discharge Summaries and ICD-9 Codes}

@@

\subsubsection{Product Descriptions and Categorizations}

Amazon.com, an online retail store, organizes its catalog of 
products in a hierarchy and provides product descriptions
for most products in their catolog.  Products can be discovered by users
through query-based searching or through product category exploration. Top-level
product categories are displayed on the front page of the website and lower
level categories can be discovered by choosing one of the top-level categories.
Products can exist in multiple locations in the hierarchy.

In this experiment, we obtained Amazon.com product categorization data from 
the Stanford Network Analysis Platform (SNAP) dataset~\citep{SNAP}. 
Product descriptions were obtained separately from the
Amazon.com website directly. We limited our dataset to the collection of DVDs
in the product catalog.

We were able to deduce the structure of the
hierarchy for the Amazon.com products because all ancestors in the
hierarchy were included with each category label. For example, {}``DVD / Genres
/ Science Fiction \& Fantasy / Classic Sci-Fi'' is a single product category 
for the DVD, {}``The Time Machine.''

@@

We applied HSLDA, along with three other closely related models, to
the clinical data and the retail product data. Specifically, we evaluate
models including sLDA with independent regressors (hierarchical constraints
on labels ignored), HSLDA fit by performing LDA followed by tree-conditional
regressions, and HSLDA fit with fixed random regression parameters. These
models were chosen to highlight several aspects of the model including performance in the absence 
of hierarchical constraints, the effect of the combined inference procedure, and regression
performance attributable solely to the hierarchical constraints.

@@

%\begin{itemize}
%\item Talk about hierarchy and no hierarchy
%\item Make explicit calculation of sensitivity and 1-specificity
%\end{itemize}

The two main methods of evaluation
for the model are prediction and topic quality. To evaluate predictive
performance for all comparison models equivalently, each model was
evaluated with two methods. The first evaluation method augments the
observed labels in the held out set with their ancestors and considers
all other non-existant labels to be negative. The second method ignores
the ancestors of the observed labels in the held out set and considers
all other non-existant labels to be negative. This uniform treatment
of ancestors allows for a fair comparison of the models.

### 2011-06-01 paper/related_work.tex
updates to multiple sections

Other models that incorporate both and some form of supervision include
LabeledLDA\citep{Ramage2009}, DiscLDA\citep{DiscLDA}, models applied to 
computer vision and document networks\citep{wangbleifeifei08,RelationalLDA}.

%One set of models that are particularly relevant to HSLDA are Chang
%and Blei's hierarchical models for document networks (Relational Topic
%Models). In that family of models, they encountered a similar scenario
%where the lack of a link did not truly indicate absence. In hierarchically
%labeled data, negative labels are uncommon and the lack of a label
%in the hierarchy is not equivalent to a negative label. Therefore,
%as in the work of Chang and Blei, we employ regularization to account
%for the lack of negative labels. This will be discussed further in
\ref{sec:model}.

>>>>

Other models that incorporate LDA and supervision include
LabeledLDA\citep{Ramage2009}, DiscLDA\citep{DiscLDA}, and other models applied to 
computer vision and document networks\citep{wangbleifeifei08,RelationalLDA}. 
These models, however, do not implement contraints on the label space.

In other work, researchers have classified documents in a hierarchy with naive Bayes classifiers
and support vector machines. Most of this work has been demonstrated on relatively
small datasets, small label spaces and has focused on single label classification without
a model of documents such as LDA\citep{mccallum99building,Dumais2000HCW,Kollerilprints291,Chakrabarti1998SFS}.

%One set of models that are particularly relevant to HSLDA are Chang
%and Blei's hierarchical models for document networks (Relational Topic
%Models). In that family of models, they encountered a similar scenario
%where the lack of a link did not truly indicate absence. In hierarchically
%labeled data, negative labels are uncommon and the lack of a label
%in the hierarchy is not equivalent to a negative label. Therefore,
%as in the work of Chang and Blei, we employ regularization to account
%for the lack of negative labels. This will be discussed further in
